---
title: "02_Data Munging"
author: "Brandon Foster, Ph.D."
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    df_print: paged
    toc: yes
    theme: paper
  html_notebook:
    number_sections: yes
    toc: yes
---

This script should walk the user through all of the steps necessary to clean and transform the final data frames for any analyses. 

 ```{r setup, include=FALSE}
 knitr::opts_knit$set(root.dir = 'rmds')
 ```

```{r, messages=FALSE, warning=FALSE}
# Load the csv data and tidy it ----
efa.data <- spss.dat %>%
  dplyr::select(id, mastercompR, nextcompR, rubricR, onlinecompR, projcredR, interncredR,
  smallgrpR, teachdifR, choosehowR, retakeR, demolearnR, adviceR, trackprogR, ontimeR, prepgradR)

# Save the tidy-ed data ----
  saveRDS(efa.data, file = "../data/efa.tidy.rds")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).
